A deeper look into bug fixes: Patterns, replacements, deletions, and additions

### 2016-02-18 MSRChallenge2016.tex
modify conclusion and PAR content

\vspace{1ex}
\noindent
{\bf Calling another overloaded method with one more parameter (COM)}. This
pattern adds one more parameter to a method. 
	{\bf Example:} obj.method(v1) $\rightarrow$ obj.method(v1,v2).
  To detect COM pattern, we create method signature similar like when detecting
  AMP and COM pattern. This time, we find whether there are exists method with
  the same name, but the number of parameters in pre-fix and post-fix version
  differs by one. If it exists, we consider that COM pattern is found.

\vspace{1ex}
\noindent
 {\bf Changing a branch condition (CBC)}. This pattern adds or removes a condition.
	{\bf Example:} if(a != b) $\rightarrow$ if(a != b \&\& c == 0).
  To detect CBC pattern, we count the number of { \em logical and} and {\em
    logical or} inside if conditional expression for both pre-fix and post-fix
  version. we assume that the addition/removal of logical operators indicate
  addition/removal of condition. If there are count differences between pre-fix
  and post-fix version, we consider that CBC pattern is found.

\vspace{1ex}
\noindent
 {\bf Initializing an object (IAO)}. This pattern adds a initialization to object declaration.
  To detect IAO pattern, we count the number of NEW expression in variable
  declaration for both pre-fix and post-fix version. If there are count
  differences between pre-fix and post-fix version, we consider that IAO pattern
  is found.
	{\bf Example:} Type obj $\rightarrow$ Type obj = new Type().

\vspace{1ex}
\noindent
 {\bf Adding a null checker (ANC)}.  This pattern inserts a condition to check whether an
    object is null or not in order to prevent unexpected state.
	{\bf Example:} obj.m1() $\rightarrow$ if(obj!=null){obj.m1()}
  To detect ANC pattern, we count the number of if conditional expression that
  contains {\em !=null} or {\em ==null} for both pre-fix and post-fix
  version. If there are count differences between pre-fix and post-fix version,
  we consider that ANC pattern is found.

\vspace{1ex}
\noindent
 {\bf Adding an array out of bound checker (AOB)}. This pattern inserts a condition to check that an array
    index is within bound right before the index is used.
	{\bf Example:} arr[idx]=0 $\rightarrow$ if(idx<arr.length){arr[idx]=0}.
  To detect AOB pattern, we count the number of if conditional expression that
  contains {\em expr<var.length} or {\em var.length>expr} for both pre-fix and
  post-fix version. If there are count differences between pre-fix and post-fix
  version, we consider that AOB pattern is found.

@@

\vspace{1ex} The above patterns only cover 8 out of 10 bug fixing patterns in
PAR. The other two patterns are: (1) checking that an object is an instance of a
target class before casting it; and (2) replacing expression in an if condition
by another expression in the same scope. Pattern (1) cannot be analyzed because
Boa does not support the {\em instanceof} expression. Similarly, pattern (2)
requires us to track scope between pre-fix and post-fix version, which is not
supported by Boa. Implementing them ourselves might be possible, but it might
require too much effort than necessary. We speculate that investigating 8 out of
10 patterns should give us a good idea on how common the patterns actually are.

@@

After running the bug pattern detection approach on Boa's dataset, we obtained
the result shown in Table~\ref{tab:freqpattern}. It shows that the
most common pattern among these patterns is CBC and the least common pattern is
AOB. If we assume that these patterns never appear together in the dataset,
these patterns cover 14.78\% of buggy files. Kim et al. mentioned that the
patterns that they use cover almost 30\% of real
patches~\cite{kim2013}. Although we only detect 8 out of 10 bug fixing patterns,
it is hard to believe that the remaining two patterns cover 15\% of buggy files,
especially 14.78\% is a number we get when we assume that the patterns that we
detect never appear together. Moreover, the percentage of each pattern is based
on imprecise approximation which is likely to represent an upper bound rather
than a lower bound. This suggests that common bug fixing patterns might not be
as common as it appeared to be.

@@

\section{Conclusions}
The findings of our study provide a set of useful guidelines for automatic
program repair tools with which their search for a patch can be now improved by
having the knowledge of how likely it is to replace a faulty statement by the
different kinds of statements available.
\todo{Expand to include summary of actual conclusions}

>>>>

\vspace{1ex}
\noindent
{\bf Calling another overloaded method with one more parameter (COM)}. This
pattern adds one more parameter to a method. 
	{\bf Example:} obj.method(v1) $\rightarrow$ obj.method(v1,v2).
  To detect COM pattern, we create method signature similar like when detecting
  AMP and COM pattern. This time, we find whether there exists method with
  the same name, but the number of parameters in pre-fix and post-fix version
  differs by one. If it exists, we consider that COM pattern is found.

\vspace{1ex}
\noindent
 {\bf Changing a branch condition (CBC)}. This pattern adds or removes a condition.
	{\bf Example:} if(a != b) $\rightarrow$ if(a != b \&\& c == 0).
  To detect CBC pattern, we count the number of { \em logical and} and {\em
    logical or} inside if conditional expression for both pre-fix and post-fix
  version. we assume that the addition/removal of logical operators indicate
  addition/removal of condition. If there is a larger count in post-fix version, we consider that CBC pattern is found.

\vspace{1ex}
\noindent
 {\bf Initializing an object (IAO)}. This pattern adds a initialization to object declaration.
  To detect IAO pattern, we count the number of NEW expression in variable
  declaration for both pre-fix and post-fix version. If there is a larger count in post-fix version, we consider that IAO pattern
  is found.
	{\bf Example:} Type obj $\rightarrow$ Type obj = new Type().

\vspace{1ex}
\noindent
 {\bf Adding a null checker (ANC)}.  This pattern inserts a condition to check whether an
    object is null or not in order to prevent unexpected state.
	{\bf Example:} obj.m1() $\rightarrow$ if(obj!=null){obj.m1()}
  To detect ANC pattern, we count the number of if conditional expression that
  contains {\em !=null} or {\em ==null} for both pre-fix and post-fix
  version. If there is a larger count in post-fix version,
  we consider that ANC pattern is found.

\vspace{1ex}
\noindent
 {\bf Adding an array out of bound checker (AOB)}. This pattern inserts a condition to check that an array
    index is within bound right before the index is used.
	{\bf Example:} arr[idx]=0 $\rightarrow$ if(idx<arr.length){arr[idx]=0}.
  To detect AOB pattern, we count the number of if conditional expression that
  contains {\em expr<var.length} or {\em var.length>expr} for both pre-fix and
  post-fix version. If there is a larger count in post-fix version, we consider that AOB pattern is found.

@@

\vspace{1ex} The above patterns only cover 8 out of 10 bug fixing patterns in
PAR. The other two patterns are: (1) checking that an object is an instance of a
target class before casting it; and (2) replacing expression in an if condition
by another expression in the same scope. Pattern (1) cannot be analyzed because
Boa does not support {\em instanceof} expression. Similarly, pattern (2)
requires us to track scope between pre-fix and post-fix version, which is not
supported by Boa. Implementing them ourselves might be possible, but it might
require too much effort than necessary. We speculate that investigating 8 out of
10 patterns should give us a good idea on how common the patterns actually are.

@@

After running the bug pattern detection approach on Boa's dataset, we obtained
the result shown in Table~\ref{tab:freqpattern}. It shows that the
most common pattern among these patterns is CBC and the least common pattern is
AOB. If we assume that these patterns never appear together,
they cover 14.78\% of buggy files. Kim et al. mentioned that the
patterns that they use cover almost 30\% of real
patches~\cite{kim2013}. Although we only detect 8 out of 10 bug fixing patterns,
it is hard to believe that the remaining two patterns cover 15\% of buggy files,
especially considering that 14.78\% is a number that we get when we assume that the patterns never appear together. Moreover, the percentage of each pattern is based
on imprecise approximation which is likely to represent an upper bound rather
than a lower bound. This suggests that common bug fixing patterns might not be
as common as it appeared to be.

@@

\section{Conclusions}
We have characterized bug fixing changes in Java.
On average, a bug fixing revision changes 11.3 files and often introduces new
fields and methods. We have also showed that 8 out of 10 bug fixing patterns in
PAR cover only 15\% of bug fixes. Last but not least, we investigated statement
level mutations and summarized the likelihood of statement insertion, deletion,
and replacement.

The findings of our study provide a set of useful insights for automatic
program repair tools in Java. It suggests that patterns in PAR are not enough to
cover the entirety of bug fixes in Java. Adding more patterns is one solution,
but may not be a permanent one. Our finding on Java bug fixes characteristic suggests that mutation based program repair may need to add new fields or methods
to fix bugs in Java and achieve a human-like written patch. A deeper look suggests
that it can also improve its search for a patch by having the knowledge of how
likely it is to replace a faulty statement by the different kinds of statements
available. Overall, our findings demonstrate that our knowledge of bug fixing
properties in Java is still lacking and therefore more research on it are
warranted.
